A statistical framework for analysing whole-genome bisulfite-sequencing data

### 2015-09-28 Rmarkdown/wgbs_statistical_framework.Rmd
Closes #23

1. There may be gaps due to the insert size being longer than the sum of the read lengths, e.g., $(i, i + 1, i + 3, i + 4)$. In effect, we have missing data for any intervening methylation loci, the $(i + 2)^{th}$ loci in this example.
2. Loci may be measured twice if the insert size is less than the sum of the read lengths, e.g. _read-1_ gives us $(i, i + 1)$ and _read-2_ gives us $(i + 1, i + 2, i + 3)$. In this example we must use only one of _read-1_ or _read-2_ as the measurement of the $(i + 1)^{th}$ locus because otherwise we are 'double-counting'.

>>>>

1. There may be gaps due to the insert size being longer than the sum of the read lengths, e.g., $(i, i + 1, i + 3, i + 4)$. In effect, we have missing data for any intervening methylation loci, the $(i + 2)^{th}$ loci in this example.
2. Loci may be measured twice if the insert size is less than the sum of the read lengths, e.g. _read-1_ gives us $(i, i + 1)$ and _read-2_ gives us $(i + 1, i + 2, i + 3)$. In this example we must use only one of _read-1_ or _read-2_ as the measurement of the $(i + 1)^{th}$ locus because otherwise we are 'double-counting'[^overlapping-mates].

[^overlapping-mates]: We should also check that the overlapping bases agree and, if not, either use the call with the highest base quality or ignore these overlapping positions in both reads. `methtuple` has several options for handling overlapping mates of paired-end reads via the `--overlap-filter` flag. The default method is to ignore any read-positions in the overlapping region where the methylation calls disagree.
